New lower bounds for Schur and weak Schur numbers

### 2021-06-06 rapport/rapport.tex
Deuxième série de corrections - partie WS

\documentclass[3p]{elsarticle}
\title{New lower bounds for Schur and weak Schur numbers}
\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}

@@

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}

@@

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. Finding templates allows us to 
get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey 
numbers \(R_n(3)\). We also developed a method to improve lower bounds for weak Schur numbers. 
Furthermore, we try to analyze former works on weak Schur numbers based on the principle that \textit{good} 
partitions into \(n+1\) weakly sum-free subsets start with a \textit{good} partition into \(n\) weakly sum-free subsets. 
We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption 
upon imposing certain conditions on the \textit{good} 5-subsets partitions. The new lower bounds include 
\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,214 \).

@@

>>>>

\documentclass{article}
\title{New lower bounds for Schur and weak Schur numbers}
\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}

@@

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}
\usepackage[a4paper, total={6in, 8in}]{geometry}

@@

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. Finding templates allows us to 
get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey 
numbers \(R_n(3)\). We also developed a new method to improve lower bounds for weak Schur numbers. 
Furthermore, this paper tries to analyze former works on weak Schur numbers based on the principle that good 
partitions into \(n+1\) weakly sum-free subsets start with a good partition into \(n\) weakly sum-free subsets. 
We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption 
upon imposing certain conditions on the good 5-subsets partitions. The new lower bounds include 
\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,214 \).

@@

\input{search_space.tex}
